---
title: "R cheet sheet"
author: "javaria"
date: "5/21/2022"
output: html_document
---

In this file we ust discuss basic things or basic functions used in R using dplyr. we'll see how to read RDS file then data tables using simple table function of base R. then we work on
checking unqiue values.

### Load Libraries

```{r}
library(tidyverse)
```

### Load dataset

```{r}
Jobs_Data <- readRDS("C:/Users/erect/Desktop/CubeStatistica/QC_PROJECT/QC_PredictiveML/VIEW_CoalesceKPIs.rds")
```

## Filter

```{r}
 filter(Jobs_Data, JobStatus == "Completed")
```

### summary

```{r}
summary(Jobs_Data$JobCompleted)
```

### table

```{r}
Jobs_Data %>% group_by(FlagColour, RedFlagStatus)%>% count()
```

### unique values

```{r}
unique(Jobs_Data$FlagColour)
unique(Jobs_Data$RedFlagStatus)

```

## table

```{r}
table(Jobs_Data$FlagColour, Jobs_Data$RedFlagStatus)
```

## convet NA to na string

```{r}
Jobs_Data$FlagColour <- Jobs_Data$FlagColour %>% replace_na('na')
head(Jobs_Data$FlagColour)
```

```{r}
Jobs_Data$RedFlagStatus <- Jobs_Data$RedFlagStatus %>% replace_na('na')
head(Jobs_Data$RedFlagStatus)
```

### make table

```{r}
table(Jobs_Data$FlagColour, Jobs_Data$RedFlagStatus)
```

## Arrange

used to sort list

```{r}
#arrange()
```

### mutate

is used to update or create new column

```{r}
Jobs_Data <- Jobs_Data %>% mutate(RedFlagged = case_when(RedFlagStatus == 'Not Ack' ~ '1'))
Jobs_Data$RedFlagged <- Jobs_Data$RedFlagged %>% replace_na(0)  
 head(Jobs_Data$RedFlagged )
```

Making new column RedFlagged

```{r}
Jobs_Data <- Jobs_Data %>% mutate(RedFlagged = case_when(RedFlagStatus == 'Not Ack' ~ '1'))

 Jobs_Data$RedFlagged <- Jobs_Data$RedFlagged %>% replace_na(0)  
```



## Add Visulization 

How to make histogram with ggplot.

```{r}
Jobs_Data %>%
    group_by(JobStatus, JobCompleted) %>%
    ggplot(aes(x =JobCompleted , fill = JobStatus)) + # `fill` is specific for histograms
        geom_histogram()
```

Bar chart with ggplot


```{r}
Jobs_Data %>%
    group_by(JobStatus,RedFlagged ) %>%
    ggplot(aes(x = RedFlagged, fill = JobStatus)) + # `fill` is specific for histograms
        geom_bar()
```

Size chart using ggplot2

```{r}
Jobs_Data %>%
    group_by(JobStatus,RedFlagged ) %>%
    ggplot(aes(x = RedFlagged,y=JobStatus, fill = JobStatus, color= RedFlagged)) + 
        geom_count()
```

Table of IsPresentInOffersTable


```{r}
Jobs_Data %>% group_by(IsPresentInOffersTable)%>% count()
```

Table for ProductName

```{r}
P_name  <- Jobs_Data%>% group_by(ProductName)%>% count()
unique(P_name$ProductName)
 sort.int(P_name$n, decreasing = TRUE)
```

get top product names 

```{r}
#library(data.table)
#order(Jobs_Data$ProductName,
     # decreasing = FALSE)
```



Some more barchart

```{r}
Jobs_Data %>%
group_by(ProductName,RedFlagStatus) %>%
    ggplot(aes(x = ProductName, fill =RedFlagStatus )) + 
        geom_bar(width = )
```



