---
title: "Intro to R Markdown"
author: "Sawera Saleem and Faizan Khalid Mohsin"
date: "2/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Creating a new R Markdown File:
1. To create an R Markdown file, go to File -> New File -> R Markdown and hit enter.
2. Enter Title and Author of the document and press ok.
3. R Markdown file with the extension of .Rmd will appear with default code and comments, which can be removed.
4. Ctrl+s to save this file and name this R Markdown file accordingly.

# Commands used in R Markdown:
There are two places to write in R Markdown files:

#### i. Code blocks:
Text written in the highlighted part/ within \```{r} 
and \``` is the code.

#### ii. Comments blocks:
Remaining text is the comments.
Different paragraphs should be written with a line differences in the .Rmd file.

# Writing code in code blocks:
1. Press ctrl+alt+i to create a block to code in.
2. Code block will be created having \```{r} 
\```

#### i. To see both code and output on R Markdown, write code in between \```{r} and 
#### \``` 
For example:
The following code 

\``` {r} 

\ summary(cars) 

\``` 

will show both code and summary of table cars.

```{r}
summary(cars)
```

#### ii. If we only want to see the output and not the code then write the code between \```{r, 
#### \ echo=FALSE } 
#### and 
#### \```
For example:
The following code 

\```
\ {r , echo=FALSE}

\ summary(cars)

\```

will show the SUMMARY of table cars and not the code.

```{r, echo=FALSE}
summary(cars)
```


# Writing Comments:
* Anything that is written out of code block will be considered are comment and will be displayed on the screen.

# Types of Headings in R Markdown:
* Heading of size 1 can be achieved by writing # before the comment.
* For heading of size 2, two hash i.e: ## will be written before the comment and so on till heading 6. 
e.g: 

# This is written in Heading size 1. In html is h1.
## This is written in Heading size 2. In html is h2.
### This is written in Heading size 3. In html is h3.
#### This is written in Heading size 4. In html is h4.
##### This is written in Heading size 5. In html is h5.
###### This is written in Heading size 6. In html is h6.

