---
title: "Intro to R Markdown"
author: "Sawera Saleem"
date: "2/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Creating a new R Markdown File:
1. To create an R Markdown file, go to File -> New File -> R Markdown and hit enter.
2. Enter Title and Author of the document and press ok.
3. R Markdown file with the extension of .Rmd will appear with default code and comments, which can be removed.
4. Ctrl+s to save this file and name this R Markdown file accordingly.

# Commands used in R Markdown:
There are two places to write in R Markdown files:

#### i. Code blocks:
Text written in the highlighted part/ within \```{r} 
and \``` is the code.

#### ii. Comments blocks:
Remaining text is the comments.
Different paragraphs should be written with a line differences in the .Rmd file.

# Writing code in code blocks:
1. Press ctrl+alt+i to create a block to code in.
2. Code block will be created having \```{r} 
\```

#### i. To see both code and output on R Markdown, write code in between \```{r} and 
#### \``` 
For example:
The following code 

\``` {r} 

\ summary(cars) 

\``` 

will show both code and summary of table cars.

```{r}
summary(cars)
```

#### ii. If we only want to see the output and not the code then write the code between \```{r, 
#### \ echo=FALSE } 
#### and 
#### \```
For example:
The following code 

\```
\ {r , echo=FALSE}

\ summary(cars)

\```

will show the SUMMARY of table cars and not the code.

```{r, echo=FALSE}
summary(cars)
```


# Writing Comments:
* Anything that is written out of code block will be considered are comment and will be displayed on the screen.

# Types of Headings in R Markdown:
* Heading of size 1 can be achieved by writing # before the comment.
* For heading of size 2, two hash i.e: ## will be written before the comment and so on till heading 6. 
e.g: 

# This is written in Heading size 1.
## This is written in Heading size 2.
### This is written in Heading size 3.
#### This is written in Heading size 4.
##### This is written in Heading size 5.
###### This is written in Heading size 6. 

# Git Commands

```{bash eval=FALSE}
#on branches

# How to initialize a folder/directory and make it a repo.
git init
git add . #add-all
git status #tells-current-branch/status-only

# How to commit to the local repo and push to remote repo.
git commit -m "commit_msg" #repo-updation-msg
git remote add origin https://github.com/sawerasaleemshaikh/___.git 
git branch #shows-all-parent-branches-with pointer-on-current-branch
git branch branch_name #creates-new-branch
git checkout branch_name #switches-to-mentioned-branch
git checkout -b branch_name #creates-&-switches-to-new-mentioned-branch,-if-it-already-exists-then-it-resets-it
git push -u origin branch_name #pushes-stuff-to-that-branch

git branch -d branchName #del local branch while being on the develop branch
git branch -D branchName #dont save changes and del local branch git push #when u
git push --delete remoteBranchName localBranchName #delete remote branch
 
#update develop: 
git add .
git commit -m ""
git push

#on main
git push -u origin master
git clone link

git pull #to get up to date with others works

git checkout branch_name #your current opened project will be closed and the one you checkedout will be opened

```



if history is making issue, open in vscode and go to extensions number and discard

no push in develop

PR made, please review.

QC-21 gauge location changed from beside graph to top.

No  errors,
No warnings,
App working fine.
