---
title: "PracticingR"
author: "Sawera Saleem"
date: "2/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reference 
### https://www.youtube.com/channel/UCcHkmB0xEm7ndGvEfSmfuqQ/playlists

## Vectors

```{r}
c()
columnName <- c() #vector
columnName
x <- 1:4
names(x) <- letters[1:4]
x

```


## creating Data frame

```{r}
x_dataFrame <- as.data.frame(x) #creates a excel kind of thing
x_dataFrame

colnames(x_dataFrame) #column names
# row.names(x_dataFrame) # row names


```

## install and load package ggplot (grammer of graphics)

```{r}
library(ggplot2) #loading package
mpg <- mpg
plot <- ggplot(mpg, aes(class))
plot + geom_bar()

```


```{r}
mpg$displ
mpg[1:3,"displ"] #returns first 3 rows (displ value only)

```


## Aggregae/sum 

```{r}

aggregate(data = mpg, displ~class, FUN=mean) #display by class
```


## install and load package dplyr
#### Pipe %>% is used to apply groub by to dataset
#### same as abaove but diff way using dplyr

```{r}
library(dplyr)
mpg %>%
  group_by(class) %>%
  summarize("Mean Displ"=mean(displ))
```



## install and load nycflights13
## filter function

```{r}
library(nycflights13)
data <- flights
head(data)
colnames(data)
# row.names(data)
filtered_data <- filter(data, tailnum=="N76515") #TAILNUM col, filter function from dplyr
filtered_data2 <- data[which(data$tailnum=="N76515"),] #without dplyr

```



## arrange function (deplyr)

```{r}
arranged_data <- arrange(filtered_data, year,month,day)

```


## rename column name using rename function (deplyr)

```{r}
data <- mpg
data <- rename(data,displacement=displ) #rename col

```

## select function (deplyr)

```{r}

small_data <- select(data,manufacturer, displacement,class) #returns only mentioned cols 

```

## mutate function (dplyr): creates, modify and del columns

```{r}
data <- flights
colnames(data)
data <- mutate(data, flight_gain=dep_delay-arr_delay,
               gain_per_hour=flight_gain/(air_time/60))

```

## group by

```{r}
by_tailnum<-group_by(data,tailnum)
#we can see difference after we apply summarize func
```


## summarise 

```{r}
summarise(data, mean_flight_gain=mean(flight_gain, na.rm=TRUE),) #NA values are not used

plane_summary<-summarise(by_tailnum, mean_flight_gain=mean(flight_gain, na.rm=TRUE),) 

```

## chaining operator

```{r}
data <- flights
data %>%
  mutate(flight_gain=dep_delay-arr_delay,
               gain_per_hour=flight_gain/(air_time/60)) %>%
  group_by(tailnum) %>%
  summarise(mean_flight_gain=mean(flight_gain, na.rm=TRUE),)


```

## datasets in R

```{r}
library(help="datasets") #shows all datasets in R
library(ggplot2)
data <- trees
ggplot(data, aes(x=Height,
                 y=Girth,
                 size= Girth))+geom_point()

data <- mpg
ggplot(data, aes(x=displ,
                 y=cty,
                 size= cyl,
                 color=class))+geom_point()

ggplot(data, aes(x=displ,
                 y=cty,
                 size= cyl,
                 color=class))+geom_point()

```

### sub (to replace first occurence in specific col)
### gsub (to replace in specific col) (global)
### trimws (trims leading and trailing white spaces)
### dfr (binds row wise)
### dfc (binds col wise)

```{r}


```

## ???

```{r}


```

## ???

```{r}


```

## ???

```{r}


```

## ???

```{r}


```

## ???

```{r}


```

## ???

```{r}


```

## ???

```{r}


```
